Model

### 2019-09-10 stats/model.Rmd
add 100k model runs

      var itemLineParameters = {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
        slope: gaussianDrift({
          mu: globalLineParameters.slope, 
          sigma: itemVariability.slope, 
          width: 0.5
        })
  //     slope: Math.pow(gaussianDrift({
  //       mu: globalLineParameters.slope, 
  //      sigma: itemVariability.slope, 
  //       width: 0.5
  //    }), 2)
      }

@@

@@

```{r}
p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source, lty = alignment), size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(condition~familiarObject)+
  facet_wrap(~item, nrow = 2)+
  #ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

@@

saveRDS(sem_know_model, "../saves/sem_know_model_variant1_100k.rds")

>>>>

      var itemLineParameters = {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
     //   slope: gaussianDrift({
     //     mu: globalLineParameters.slope, 
      //    sigma: itemVariability.slope, 
      //    width: 0.5
     //   })
      slope: Math.pow(gaussianDrift({
         mu: globalLineParameters.slope, 
        sigma: itemVariability.slope, 
         width: 0.5
      }), 2)
      }

@@

#saveRDS(sem_know_model, "../saves/sem_know_model_variant2_100k.rds")
```

@@

```{r}
p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source, lty = alignment), size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(condition~familiarObject)+
  facet_grid(~item)+
  #ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

@@

#saveRDS(sem_know_model, "../saves/sem_know_model_variant2_100k.rds")
